---
title: "BullpenApp Project Script"
output: html_notebook
---

**BullpenApp Project Script**
Carter Hall 

*Ideas*
- Homepage 
  - Welcome Message :)
  - Basic Stats for Most Recent Session
    (Pie Chart of Pitch Types, Session History, Max Velo, Max RPM, Recent Notes)
     
- Option Tab
  - Checkboxes Here, Menus Here

- Pitch Plot for Session (Location, SZ)
  - CheckboxGroup for Session Date(s)
  - CheckboxGroup for Warmup/Live (Live standard opt.)
  - SZ Toggle
  - Baseball Image Toggle???
  
- Line Graph (Check Consistency, Duration of Sustaining XX mph Velo, XXXX RPMs, etc.)
  - Use CG for Session Date(s)
  - Dropdown to Specify Metric(s)
     - Limit 2-3? Use 320 Stuff to Section Graph (GGPlot... Future Conversion to Plotly? )


```{r Libraries, message = FALSE, warning = FALSE}
options(shiny.maxRequestSize = 50*1024^2)
library(shiny)
library(shinydashboard)
library(DT)
library(ggplot2)
library(dplyr)
library(Jmisc)
library(msm)
library(gt)
library(leaflet)
require(shinythemes)
```

```{r UI}
ui <- navbarPage(
    title = "The Tar Pen",
    theme = shinytheme("lumen")
  
)
```


```{r Server}
server <- function(input, output, session) {
  
}

shinyApp(ui, server)
```

