---
title: "BullpenApp Project Script"
---

**BullpenApp Project Script** 
Carter Hall 

*Ideas* 
- Homepage 
- Welcome Message :)
- Basic Stats for Most Recent Session
(Pie Chart of Pitch Types, Session History, Max Velo, Max RPM, Recent Notes)

- Option Tab
- Checkboxes Here, Menus Here

- Pitch Plot for Session (Location, SZ)
- CheckboxGroup for Session Date(s)
- CheckboxGroup for Warmup/Live (Live standard opt.) --> Implement this in Server
- SZ Toggle
- Baseball Image Toggle???

- Line Graph (Check Consistency, Duration of Sustaining XX mph Velo, XXXX RPMs, etc.)
- Use CG for Session Date(s)
- Dropdown to Specify Metric(s)
- Limit 2-3? Use 320 Stuff to Section Graph (GGPlot... Future Conversion to Plotly? )


```{r Libraries, message = FALSE, warning = FALSE}
options(shiny.maxRequestSize = 50*1024^2)
library(shiny)
library(shinydashboard)
library(DT)
library(ggplot2)
library(dplyr)
library(shinythemes)
```

```{r Functions message = FALSE, warning = FALSE}
library(DBI)
library(dbplyr)
library(RSQLite)

queryDB <- function(query) {
  return(dbGetQuery(db, query))
}

obtainSession <- function(player) {
  q <- "SELECT DISTINCT Date FROM TestData WHERE Pitcher = '_'"
  result <- list(unname(queryDB(gsub(pattern = '_', replacement = player, x = q)))[[1]])
  names(result) <- result
  return(result)
}
```

```{r UI}
ui <- dashboardPage(
  title = "The Tar Pen",
  header = dashboardHeader(),
  sidebar = dashboardSidebar(
    sidebarMenu(
    menuItem(text = "Start Here", 
             tabName = "start",
             icon = icon("home"))
    )
  ),
  body = dashboardBody(
    
    tabItems(
      
      tabItem(
        tabName = "start",
        
        fluidRow(
          column(
            
            width = 3,
            offset = 0,
            
            h3("Player Name"),
            selectInput(inputId = "playerSelect",
                        label = NULL,
                        choices = NULL)
            ),
            
          column(
            width = 3, 
            offset = 0,
            
            h3("Session Date"),
            selectizeInput(inputId = "sessionSelect",
                           label = NULL,
                           choices = NULL)
            ),
          
          column(
            width = 2, 
            offset = 0,
            
            h3("Warmup/Live/Both?"),
            checkboxGroupInput(inputId = "warmupLiveSelect",
                               label = NULL,
                               choices = c("Warmup" = "w",
                                           "Live" = "l")
            )
            
          )
        ),
        
        fluidRow(
          
          box(title = "Pitch Locations"),
          box(title = "Velo & Spin Graphs")
          
        ),
        
        fluidRow(
          box(title = "Previous Notes",
              width = 9),
          box(title = "Add Notes", 
              width = 3)
        )
      )
    )
  )
)
```

```{r Server}
server <- function(input, output, session) {
  
  flags <- reactiveValues(ps = NULL, ss = NULL, w = NULL, l = NULL)
  
  updateSelectInput(
    
    session = session,
    inputId = "playerSelect",
    # QUERY: Return all names of pitchers in alphabetical order.
    choices = queryDB("SELECT DISTINCT Pitcher FROM TestData
                              ORDER BY Pitcher ASC"),
    selected = NULL
    
  )
  
  observeEvent(input$playerSelect,
               {
                 flags$ps <- input$playerSelect
                 
                 updateSelectizeInput(session = session,
                                      inputId = "sessionSelect",
                                      # QUERY: For a pitcher, obtain
                                      #        all dates of prev. sessions.
                                      choices = obtainSession(flags$ps)
                 )
                 
                 flags$ss <- input$sessionSelect
                 
               }
  )
  
  observeEvent(input$warmupLiveSelect, 
               {
                 # When using, check if not NA
                 flags$w <- input$warmupLiveSelect[1]
                 flags$l <- input$warmupLiveSelect[2]
               })
  
  session$onSessionEnded(function() {
    dbDisconnect(db)
  })
}
```

```{r Database}
# Run This Code Before shinyApp()
db <- dbConnect(RSQLite::SQLite(), "data.sqlite")

suppressWarnings( 
  expr = {
    cols <- names(queryDB("SELECT * FROM TestData"))
    for (col in cols) {
      q <- gsub(pattern = "_", replacement = col, x = "UPDATE TestData SET _ = NULL WHERE _ = '' ")
      queryDB(q)
    }
  }
)
```

```{r Main}
shinyApp(ui, server)
```

